Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-01 doc/PRF2022/PRF_main.tex
working on results

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent. The particles
are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \dots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

@@

To calculate the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the
free energy~\cite{Fu20}, we compute the variation of the domain of the
free energy~\eqref{eq:free_energy} subject
to~\eqref{eq:SL}--\eqref{eq:SLbc}, and obtain 
\begin{align}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{align}
for $i = 1,\dots,N_b$ with particle outward normal $\nnu$, where
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
\end{align}
is the hydrophobic stress. The repulsion is rotationally symmetric and
does not contribute to the torque.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representation and time stepping}
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the first kind, and $\sigma$ is
a scalar-valued density function. The subscript in $\dif s_\yy$ denotes
integration with respect to $\yy \in \Gamma$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
    \xx \in \Gamma.
\end{align}

For the velocity, we use the representation
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $2NN_b \times 2NN_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES, and we guarantee that the
number of GMRES iterations is mesh-independent by using second-kind
BIEs.

\todo[inline]{BRYAN IS HERE}
%Once the translational and angular velocities $\vv_i, \omega_i$
%have been determined, a second-order Adams-Bashforth scheme updates the particle
%positions and orientations:
%\begin{equation}
%  \label{eq:adams-bashforth}
%  \begin{aligned}
%    \aa_i(t_{n+2}) &=
%\aa_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
%    \theta_i(t_{n+2}) &=
%\theta_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
% \end{aligned}
%\end{equation}

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientations and the inset shows $N_b=60$ particles configuration.
  The particles self-assemble into distinct configurations,
  depending on the boundary condition \eqref{eq:bc-type}.
  Panel (b) is for $b=1$ and the boundary condition mimics that
  of an amphiphilic particle giving bilayer structures. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
  The inset in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
  as the main panels.}
\end{caption}
\end{figure}

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary conditions of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  2\pi c$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP surface.
Then, the boundary condition (BC) can be classified into
three categories: $\min g >0$, $\min g =0$, and $\min g <0$.  
These three categories correspond to three characteristic
values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles and 60 particles in a quiescent flow as shown in Fig~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayer for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Fig~\ref{fig:relax}(a) shows the initial configurations with
orientations of the 198-particle and 60-particle cases,
respectively. 
BC (i) with $b = 1$ mimics an amphiphilic particle.
The boundary data $g$ is everywhere nonnegative,
and takes
the maximum value $a$ on the hydrophobic tail (red)
the value $0$ on the hydrophilic head (green). 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Fig~\ref{fig:relax}(b)). The inset shows the equilibrium 
state for the 60-particle run.
Both cases form bilayers with multiple components.

In BC (ii) with $b = 1$, the boundary data is everywhere positive.
It takes the maximum value $3a$ on the tail (red) and the
minimum value $a$ on the head side (yellow). 
Both sides of the Janus particle are hydrophobic but
more so on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for  (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures\cite{C9NR05885K}.
The number of folds depends primarily on the number of particles.
Fig~\ref{fig:relax}(c), for example, shows a
multilamellar structure with four layers and one with two layers in the inset.

Finally, BC (iii) with $b=1$ 
corresponds to a water structure with
positive/negative charge \cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
square grid and the orientations alternate
between layers (Fig~\ref{fig:relax}(d)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Fig \ref{fig:relax}(a)
    and the final energies are for the near-equilibrium
    configurations as shown in Fig \ref{fig:relax}(b)--(d), respectively.
    The solid curves are the energies for the $N_b=60$ cases and  
    the dashed curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. 
    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel (a).
    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
    The results of the striated configuration, however, depend on the initial geometrical setup.
  }
\end{figure}

@@

First, we must simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are given.
However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See Appendix in \S\ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.
We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
the primal energy \eqref{eq:free_energy} along test curves placed slightly
outside the particles.

Fig~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
For the 198-particle cases, we normalized the energies by 60/198 and the results
show that all energies decrease with good agreements in all boundary conditions (dashed curves).
This can be considered as evidence that the free energy per particle with specified
boundary conditions is independent of the total particle number $(N_b)$.

>>>>

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\DDD}{\boldsymbol{\mathcal{D}}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\ee}{\mathbf{e}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The Janus particles are suspended in a viscous solvent. The particles
are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
viscosity. The solvent velocity satisfies the no-slip boundary condition
for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

@@

To calculate the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the
free energy~\cite{Fu20}, we compute the variation of the domain of the
free energy~\eqref{eq:free_energy} subject
to~\eqref{eq:SL}--\eqref{eq:SLbc}, and obtain 
\begin{align}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{align}
for $i = 1,\ldots,N_b$ with particle outward normal $\nnu$, where
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
\end{align}
is the hydrophobic stress. The repulsion is rotationally symmetric and
does not contribute to the torque.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representation and time stepping}
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the first kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \Gamma$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
    \xx \in \Gamma.
\end{align}

For the velocity, we use the representation
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $2NN_b \times 2NN_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES, and we guarantee that the
number of GMRES iterations is mesh-independent by using second-kind
BIEs. Once the translational and rotational velocity are computed, the
position and orientation of each JP is updated using the second-order
Adams-Bashforth scheme.

%Once the translational and angular velocities $\vv_i, \omega_i$
%have been determined, a second-order Adams-Bashforth scheme updates the particle
%positions and orientations:
%\begin{equation}
%  \label{eq:adams-bashforth}
%  \begin{aligned}
%    \aa_i(t_{n+2}) &=
%\aa_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
%    \theta_i(t_{n+2}) &=
%\theta_i(t_{n+1})
%+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
%- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
% \end{aligned}
%\end{equation}

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random
  positions and orientations and the inset shows a $N_b=60$ particles
  configuration. The particles self-assemble into distinct
  configurations, depending on the boundary
  condition~\eqref{eq:bc-type}. Panel (b) is for $b=1$ and the boundary
  condition mimics that of an amphiphilic particle giving bilayer
  structures. Panel (c) is for $b=2$ which gives rise to a
  multilamellar configuration. In panel (d), the case $b = 0$ is for a
  water structure with positive/negative charge. The false color maps
  use blue for $u < 0$, green for $u = 0$, and yellow then red for $u >
  0$. The inset in panels (b)--(d) are configurations using $N_b=60$ and
  share the same color map as the main panels.}
\end{caption}
\end{figure}

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
We consider boundary conditions of the form
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  2\pi c$.
The motivation for this normalization is that the hydrophobic attraction
part of the free energy converges to the integral of the square of the boundary
data in the zero-screening length limit.  
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
surface.  Then, the boundary condition (BC) can be classified into three
categories: $\min g >0$, $\min g =0$, and $\min g <0$.  These three
categories correspond to three characteristic values of $b$ in
\eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
%
To see the effect of the shift parameter $b$, we simulate the dynamics
of 198 particles and 60 particles in a quiescent flow as shown in
Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
bilayer for $b = 1$, (ii) multilamellar for $b = 2$, and (iii) striated
for $b = 0$.

Figure~\ref{fig:relax}(a) shows the initial configurations with
orientations of the 198-particle and 60-particle cases, respectively.
BC (i) with $b = 1$ mimics an amphiphilic particle. The boundary data
$g$ is everywhere nonnegative, and takes the maximum value $a$ on the
hydrophobic tail (red) the value $0$ on the hydrophilic head (green).
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers (Figure~\ref{fig:relax}(b)). The
inset shows the equilibrium state for the 60-particle run. Both cases
form bilayers with multiple components.

In BC (ii) with $b = 1$, the boundary data is everywhere positive. It
takes the maximum value $3a$ on the tail (red) and the minimum value $a$
on the head side (yellow). Both sides of the Janus particle are
hydrophobic but more so on the $\alpha = 0$ side. Over a short time
scale, these particles also self-assemble into bilayers. But unlike for
BC (i), the heads are also hydrophobic and so in the long-time dynamics
these bilayers form multilamella structures~\cite{C9NR05885K}. The
number of folds depends primarily on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
with four layers and one with two layers in the inset.

Finally, BC (iii) with $b=1$ corresponds to a water structure with
positive/negative charge~\cite{MaRa76, Ma77}. Here, the head repels the
tail of other particles and the particles initially form chains with
their directors perpendicular to the length of the chain. The chains
form stria where the particles lie on a square grid and the orientations
alternate between layers (Figure~\ref{fig:relax}(d)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}
  \todo[inline]{We should capitalize bc is that it reads BC like we have
  in the text.}
  \caption{\label{fig:relax_energy}
  Panel (a) shows that the free energy~\eqref{eq:free_energy} decreases
  in the mobility problem formulation. The initial energies are for the
  configuration in Figure~\ref{fig:relax}(a) and the final energies are
  for the near-equilibrium configurations shown in
  Figures~\ref{fig:relax}(b)--(d). The solid curves are the energies for
  the $N_b=60$ cases and the dashed curves are the energies for the $N_b
  = 198$ cases normalized by $60/198$, showing that the energy
  approximately scales with the number of particles.  Panel (b) shows
  the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs.
  The curve styles are identical those in panel (a). The
  near-equilibrium configurations depend on the initial configurations
  and the results show that for both $N_b=60$ and $N_b=198$ cases,
  bilayer and multi-lamellar configurations have similar trends in
  orientational parameters. The results of the striated configuration,
  however, depend on the initial geometrical setup.}
\end{figure}

@@

First we simplify the form of the free energy~\eqref{eq:free_energy}.
Using integration by parts and~\eqref{eq:SL}, we obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are
given. However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based
on~\eqref{eq:SL_BIE} involves calculating a quadruple layer potential
which has a well-known obstacle in numerical implementation.  To
overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, $\tt(\xx)$ is the tangent vector and $\dif/\dif s$ is the
arclength derivative. See the Appendix in \S\ref{sec:appendix} for the
proof and details. Substituting~\eqref{eq:normal_deriv}
into~\eqref{eq:free_energy2} for the normal derivative leads to the
single layer, $\SS$, which is more straightforward to evaluate and we
compute the arclength derivative using spectrally accurate Fourier
transform. We have validated the form of~\eqref{eq:normal_deriv} by
extrapolating the primal energy~\eqref{eq:free_energy} along test curves
placed slightly outside the particles.

Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all
relaxation runs.  For the 198-particle cases, we normalized the energies
by 60/198 and the results show that all energies decrease with good
agreements in all boundary conditions (dashed curves).  This can be
considered as evidence that the free energy per particle with specified
boundary conditions is independent of the total particle number $(N_b)$.
